IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-05-11 paper/retrofit.tex
Improve notation.

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
}
{|
niconf iS  id il (send id' il' iv)
->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| (filter il (iS(id))) = io1 , ... , iok , (il', id', iv)|\\
| iS' = bracket iS (mapsto id (io1 , ... , iok))|\\
}
{|
niconf iS  id il (recvf ix1 ix2 ie1 ie2)
->
niconf iS' id il ({iv/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = bracket iS (mapsto id nil)|
}
{|
niconf iS  id il (recvf ix1 ix2 ie1 ie2)
->
niconf iS' id il ie2
|}

>>>>

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|readState iS (id') = Q|\\
|iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
}
{|
niconf iS  id il (send id' il' iv)
->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| (filter il (readState iS id)) = io1 , ... , iok , (il', id', iv)|\\
| iS' = bracket iS (mapsto id (io1 , ... , iok))|\\
}
{|
niconf iS  id il (recvf ix1 ix2 ie1 ie2)
->
niconf iS' id il ({iv/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (readState iS (id)) = nil|\\
| iS' = bracket iS (mapsto id nil)|
}
{|
niconf iS  id il (recvf ix1 ix2 ie1 ie2)
->
niconf iS' id il ie2
|}
